Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-03-06 SupportingInformation.Rmd
Finished this round of edits except for the Discussion, which we are still working on. Some notes for Shya.

pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf",height=4,width=16)
op<-op<-par(mfrow=c(1,4),mar=c(4,5,1,1),mgp=c(3,1,0))
##plot TL for clayton
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(kend.points.res[[1]][,1,1],kend.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[1]][,1,2],kend.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black")

@@

pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf",height=4,width=16)
op<-op<-par(mfrow=c(1,4),mar=c(4,5,1,1),mgp=c(3,1,0))
##plot TL for clayton
plot(spea.points.res[[1]][,1,],spea.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(spea.points.res[[1]][,1,1],spea.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[1]][,1,2],spea.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black")

@@

\begin{figure}[!h]
\textbf{ \hspace{2.8 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.6 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=18 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf}\\
\end{center}
\textbf{ \hspace{1.8 cm} (E) \hspace{1.6 cm} (F) \hspace{1.8 cm} (G) \hspace{1.8 cm} (H) \hspace{1.8 cm} (I) \hspace{1.8 cm} (J) \hspace{1.8 cm} (K)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=18 cm]{./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf}
\caption[Spatial Taylor's Law results]{Spatial Taylor's Law results: log(spatial variance) vs. log(spatial mean) for $ns=1000$ number of (A) Clayton, (B) Normal, (C) Frank, (D) Survival Clayton surrogates; (E) p-value for test of linearity, (F) p-value for test of homoskedasticity, (G) root mean square error, (H) intercept, (I) slope, (J) quadratic coefficient, (K) mean curvature of regression line from first panel-plots. \label{fig_spTL}}
\end{center}
\end{figure}

@@

- Given data $x_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$, let $\tau_{ij}$ be the Spearman (or Kendall) 
correlation of $x_i(t)$ and $x_j(t)$.
- Calculate the covariance matrix of a multivariate normal distribution with standard-normal
marginals and with pairwise Spearman (or Kendall) correlations equal to the $\tau_{ij}$. This is possible
using the `iRho` function (or the `iTau function) of the `VineCopula` package
- Generate data $a_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$ by taking $T$ independent draws
from the the multivariate normal distribution of the previous step.
- For any $i,t$ for which the datum $x_i(t)$ was missing, replace $a_i(t)$ by `NA`.
- For each $k$ and $i$ for which $a_i(t)$ is not `NA`, replace the 
$k$th-smallest (non-`NA`) element of the time series 
$a_i(t)$, $t=1,\ldots,T$ by the $k$th smallest (non-`NA`) 
element of $x_i(t)$, $t=1,\ldots,T$.
Call the result $b_i(t)$. This is a surrogate dataset.

@@

\noindent Pursuing ideas that sprang from earlier theoretical work [@Reuman2017], we 
tested whether the copula structure of dependence between population variables 
measured in different locations influences the spatial version of Taylor's
law. Taylor's law is an extremely commonly observed and widely studied 
[@Taylor1961; @Taylor1988; @Cohen2013; @Xu2016] empirical pattern that relates the 
variances of groups, $g$, of population measurements to the means of the 
groups via a power law, $v_g = a \times m_g^b$, or equivalently, 
$\log(v_g)=\log(a)+b \times \log(m_g)$. Here $b$ is called 
the Taylor's law *exponent* or 
*slope*. There are several versions of Taylor's law. For spatial Taylor's law,
given population density or abundance data $x_i(t)$ measured in locations
$i=1,\ldots,N$ and times $t=1,\ldots,T$, a group $g$ consists of 
all the measurements $x_i(t)$, $i=1,\ldots,N$ made in different locations at the same time.
So means and variances are computed across space. Taylor's law has been 
verified empirically for hundreds of taxa and has been applied in numerous fields
including fisheries management, estimation of species persistence times, and
agriculture [@Cohen2015; @Reuman2017].

We examined using simulations whether copula structure influences spatial Taylor's law as 
follows. First, an $n \times n$ covariance matrix $\Sigma$ was created
with unit diagonal entries 
and off-diagonal entries $\rho=0.7$; $n=25$ was the number of locations at which populations
were sampled. Then $N \times 1000$ random vectors were generated from a multivariate normal 
distribution with mean vector $(0,\ldots,0)$ and covariance matrix $\Sigma$. These 
were organized into an $N \times n \times 1000$ array representing $1000$ simulations of 
populations measured in $n$ locations over $N$ time steps. 
The cumulative distribution function
(cdf) of the standard normal distribution was applied to these numbers, followed by the 
inverse of the cdf of a gamma distribution with shape and scale parameters $7.5$ and $1$. 
These transformations made gamma distributed the marginal distributions of 
each population sampling location in each simulation. 
A skewed population marginal distribution is an 
important factor in Taylor's law [@Cohen2015; @Reuman2017]. We refer henceforth to the 
resulting $N \times n \times 1000$ array as our *N array* for this simulation exercise;
copula structure of dependences between populations in different sampling locations
was normal (N) for the simulations in this array.

We then considered an $n$-dimensional C copula with parameter chosen so that the 
Kendall correlations between each pair of the $n$ components were the same as those
of the N distribution constructed above.

the nature of the slope and how it changed if population time series (taken as $50$ years) from different locations (say, $numloc=25$) had some certain type of copula structure (namely, \textbf{C}, \textbf{F} and \textbf{SC}) other than the $\textbf{N}$ormal copula. First, we simulated (N $\times$ n $\times$ nr) dimensional normal copula with co-variance $\rho =0.7$, where $(N=50,n=25,nr=10)$ are the length of time series, number of sampling locations and number of replica for that copula, respectively. Then we generated Kendall-correlation preserving \textbf{C}layton, \textbf{F}rank and $\textbf{S}$urvival \textbf{C}layton surrogates with same dimension of \textbf{N}ormal. With these four different types of copula we computed `log`(spatial variance) and `log`(mean) and plotted in Fig.\ref{fig_spTL}(A-D). We also tested statistically that whether linearity, homoskedasticity is maintained in each copula data set or not and plotted our results along with root mean square error, intercept and slope in Fig.\ref{fig_spTL}(E-I). We did a quadratic regression with each simulated copula for all types and measured quadratic coefficient and mean curvature for the regression line which is plotted in Fig.\ref{fig_spTL}(J-K) (For code see [`copsurrognd.R`](https://github.com/sghosh89/BIVAN/blob/master/copsurrognd.R) and [`TaylorsLawTools.R`](https://github.com/sghosh89/BIVAN/blob/master/TaylorsLawTools.R)).

<!--
Curvature calculations:
***DAN: Shya, I need a reminder how we did this, can you please tell me where the
code is, then I can write this section. Feel free to take a stab at it yourself, too,
though.
***Shya: What do you want to know? how did you calculate mean curvature and 
slope for made up data or you want to see code with real data?

In case of made up data :
For each non-N copula family (C,F,SC) you generated surrogates
having similar correlation (spearman/ kendall, though for 
consistency we added plots in suppmat with spearman) that of N copula
[using copsurrognd.R] : this thing is done in r chunk named "taylors_law_make_surrogs".

Then you did spatial-TL calculation for each set of copula family in r chunk "tl_analysis"
[using TaylorsLawTools.R which calls mncurvat.R code to calculate mean curvature]

Next two r chunks : taylor_plots_kendall and taylor_plots_spearman generates plot with those data.

For spatial TL calculation on real data :

We used Aphid count all sp with spearman only, but to show a plot for example chose sp=6 (corn leaf aphid)
as it had significant p_left value for mean curvature.
code is in r chunk named "spatialTL_on_realdata_aphid_count".
-->

<!--
Stuff on TL cut from the main text
From Q3 methods:
We tested whether the linearity of the spatial Taylor's law relationship was partly
due to the copula structure of the dependences between the populations sampled. 
Using corn leaf aphid abundance data as an example, but also
applying the same analysis to the abundance data we had for 19 other aphid species
(see *Data*), we calculated the curvature (details in Appendix \ref{SM-TL_curvature}) 
of the empirical Taylor's law relationship; Taylor's law hypothesizes that this 
curvature should be close to 0. We then calculated the same curvature quantity for
10000 surrogate datasets, using the same surrogate procedure described above in 
this section, and compared the empirical Taylor's law curvature to the 
distribution of surrogate curvatures using a two-tailed test. If the empirical
curvature value was below the $5^{\text{th}}$ quantile of the surrogate distribution, 
then copula structure contributes to the linearity of spatial Taylor's law 
because randomizing copula structure while retaining other statistical properties
of the data cause the Taylor's law relationship to become significantly more 
curved.

From Q3 results:
```{r read_tl_aphid_count_sp6, echo=F}
tlsp6<-readRDS("./Results/taylorslaw_results/tl_aphid_count_sp6.RDS")
tl_aphid_count<-readRDS("./Results/taylorslaw_results/tl_aphid_count.RDS")
aphid_info<-readRDS("./Results/aphid_info.RDS")
pleft<-tl_aphid_count$p_left_mncurv
stat<--2*sum(log(pleft))
pchi2<-1-pchisq(stat,40)
idsp<-which(pleft<0.05)
pleftgood<-pleft[idsp]
```

Results also suggested that copula structure contributes to the linearity of 
spatial Taylor's law. For instance, the spatial Taylor's law relationship 
for corn leaf aphid abundance data was significantly less curved than for 
surrogate datasets (Fig. \ref{fig_sTL_mncurv_sp6}). Three of $20$ aphid species
had cuvatures less than at least $95\%$ of surrogate datasets ($p=$ `r pleftgood` for 
the `r aphid_info$c1[idsp]` species, respectively). 
***DAN: Shya, please fill in X, Y, Z, A, B, C with autolinks)
***Shya: Done.
Three such significant
results of 20 species could have occurred by chance due to 
multiple-testing error. However, for each of the 20 species, we computed the fraction
of surrogate curvatures less than the curvature that came from real data, and we
combined these $p$-values using Fisher's combined probability test to get an
aggregate $p$-value of `r pchi2`
***DAN: Shya, see the Wikipedia article on Fisher's method to learn about it. Then 
you need to put this analysis into the code suite and have the resulting p value
typed in above be an autolink instead. Here is what I did: 
1) I copied by hand all the pleft values on the pdf you sent me into a vector pleft. Instead you should create such a vector in your code from your test output, not typing in the results.
2) I used the formula stat<--2*sum(log(pleft)) to get the Fisher method statistic
3) I compared to a chi-squared distribution with 40 degress of freedom using 1-pchisq(stat,40) to get my p-value
Please let me know if any of this is unclear.
***Shya: Done.
for the test of the null hypothesis that 
copula structure did not contribute to linearity of Taylor's law for any of the 
species. This result is usefully suggestive and can guide future work, but still does not
provide certainty, because the Fisher method provides $p$-values that are too 
small if its assumption of independent tests is violated. Though our 20 species
have different host plants so may be independent for the purposes of our analyses, 
it would be difficult to fully assess independence.
***DAN: Shya, can you remind me why the same analyses were not done for plankton,
if there is a good reason? Or if you did it, what were the results?
***Shya : we did it, I have the pdf but I don't have the code where I called to generate the pdf,
As we could not get any significant results for a single species (see attachment in the mail I sent you)
we did not show the results. 
We provide simulation results in Appendix \ref{SM-Consequence_TL_simulation}
that robustly illustrate, at least in the model setup we used, 
that copula structure influences spatial Taylor's law.

\begin{figure}[!h]
\textbf{ \hspace{4 cm} (A) \hspace{4 cm} (B) \hspace{4 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=10 cm]{./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf}
\includegraphics[width=5 cm]{./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf}\\
\caption{Mean curvature of the spatial Taylor's law relationship for 
corn leaf aphid abundance
data (A) was significantly less than for surrogates (B, C). The Taylor's law 
relationship for one example surrogate (B) shows shows greater curvature than
for data (A), and the significance of the difference was demonstrated
by the fact that only `r (tlsp6$p_left_mncurv)*10000` of $10000$ surrogates had curvature less than that
of the data (C). See Appendix \ref{SM-TL_curvature} for details on 
how curvature was calculated.\label{fig_sTL_mncurv_sp6}}
\end{center}
\end{figure}
***DAN: Shya, pls make the x axis label on C read simply "Mean curvature"
***Shya: dONE.
-->

>>>>

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.png",width=16,height=4,units="in",res=400)
op<-op<-par(mfrow=c(1,4),mar=c(4,5,1,1),mgp=c(3,1,0))
##plot TL for clayton
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(kend.points.res[[1]][,1,1],kend.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[1]][,1,2],kend.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black")

@@

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png",height=4,width=16,units="in",res=400)
op<-op<-par(mfrow=c(1,4),mar=c(4,5,1,1),mgp=c(3,1,0))
##plot TL for clayton
plot(spea.points.res[[1]][,1,],spea.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(spea.points.res[[1]][,1,1],spea.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[1]][,1,2],spea.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black")

@@

\begin{figure}[!h]
\textbf{ \hspace{2.8 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.6 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=18 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png}\\
\end{center}
\textbf{ \hspace{1.8 cm} (E) \hspace{1.6 cm} (F) \hspace{1.8 cm} (G) \hspace{1.8 cm} (H) \hspace{1.8 cm} (I) \hspace{1.8 cm} (J) \hspace{1.8 cm} (K)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=18 cm]{./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf}
\caption[Spatial Taylor's law results]{Spatial Taylor's law results. Log(spatial variance) vs. 
log(spatial mean) relationships for $1000$ simulations over $50$ time steps for $25$ locations 
using Clayton (A), normal (B), Frank (C), and survival Clayton (D) copula structures between
locations. Results from all $1000$ 
simulations were plotted on the same axes for each panel, but two example simulations are 
shown in red and green to help assess to what extent variation on the plots was between 
simulations or within simulations. For each simulation, we tested the linearity 
(E) and homoskedasticity (F) of the log(variance) vs. log(mean) plot for that simulation, 
and quantified the root mean squared error of points from the linear regression line (G).
We also calculated the linear regression intercept (H) and slope (I), the quadratic
term of a quadratic regression through the points on the log(variance) vs. log(mean) plot
(J), and the curvature of that quadratic regression (K). Distributions of values 
across all 1000 simulations are displayed. Spearman-preserving surrogates were used, 
though results using Kendall-preserving surrogates were very similar. See 
Appendix \ref{Consequence_TL_simulation} for 
simulation and plotting details.\label{fig_spTL}}
\end{center}
\end{figure}

@@

- Given data $x_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$, let $\tau_{ij}$ be the Spearman (or Kendall) 
correlation of $x_i(t)$ and $x_j(t)$.
- Calculate the covariance matrix of a multivariate normal distribution with standard-normal
marginals and with pairwise Spearman (or Kendall) correlations equal to the $\tau_{ij}$. This is possible.
using the `iRho` function (or the `iTau` function) of the `VineCopula` package
- Generate data $a_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$ by taking $T$ independent draws
from the multivariate normal distribution of the previous step.
- For any $i,t$ for which the datum $x_i(t)$ was missing, replace $a_i(t)$ by `NA`.
- For each $k$ and $i$ for which $a_i(t)$ is not `NA`, replace the 
$k$th-smallest (non-`NA`) element of the time series 
$a_i(t)$, $t=1,\ldots,T$ by the $k$th smallest (non-`NA`) 
element of $x_i(t)$, $t=1,\ldots,T$.
Call the result $b_i(t)$. This is a surrogate dataset.

@@

\noindent Pursuing ideas that sprang from earlier theoretical work [@Reuman2017], we 
tested whether the copula structure of the dependences between population variables 
measured in different locations influences the spatial version of Taylor's
law. Taylor's law is an extremely commonly observed and widely studied 
[@Taylor1961; @Taylor1988; @Cohen2013; @Xu2016] empirical pattern that relates the 
variances of groups, $g$, of population measurements to the means of the 
groups via a power law, $v_g = a \times m_g^b$, or equivalently, 
$\log(v_g)=\log(a)+b \times \log(m_g)$. Here $b$ is called 
the Taylor's law *exponent* or 
*slope*, and we refer to $\log(a)$ as the Taylor's law intercept. 
There are several versions of Taylor's law. For spatial Taylor's law,
given population density or abundance data $x_i(t)$ measured in locations
$i=1,\ldots,N$ and times $t=1,\ldots,T$, a group $g$ consists of 
all the measurements $x_i(t)$, $i=1,\ldots,N$ made in different locations at the same time.
So means $m_g$ and variances $v_g$ are computed across space. We view the assumptions
of Taylor's law to be validated for a dataset if the 
$\log(v_g)$ versus $\log(m_g)$ scatter plot 
for the dataset shows a linear, homoskedastic pattern.
Taylor's law has been 
verified empirically for hundreds of taxa and has been applied in numerous fields
including fisheries management, estimation of species persistence times, and
agriculture [@Cohen2015; @Reuman2017].

We examined using simulations whether copula structure influences spatial Taylor's law, as 
follows. First, an $n \times n$ covariance matrix $\Sigma$ was created
with unit diagonal entries 
and off-diagonal entries $\rho=0.7$; $n=25$ was the number of locations at which populations
were sampled. Then $N \times 1000$ random vectors were generated from a multivariate normal 
distribution with mean vector $(0,\ldots,0)$ and covariance matrix $\Sigma$. These 
were organized into an $N \times n \times 1000$ array representing $1000$ replicate 
simulations of (temporally independent, in this example) 
spatio-temporal population dynamics measured in 
$n$ locations over $N$ time steps. We used $N=50$.
The cumulative distribution function
(cdf) of the standard normal distribution was applied to these numbers, followed by the 
inverse of the cdf of a gamma distribution with shape and scale parameters $7.5$ and $1$. 
These transformations made gamma distributed the marginal distributions of populations in 
each sampling location for each simulation. 
A skewed population marginal distribution is an 
important factor in Taylor's law [@Cohen2015; @Reuman2017]. We refer henceforth to the 
resulting $N \times n \times 1000$ array as our *N-copula population array* 
for this simulation exercise;
copula structure of dependences between populations in different locations
was normal (N) for this array.

We then generated an series of arrays that were the same dimensions ($N \times n \times 1000$)
as the N-copula population array, and that were statistically similar to 
the N-copula population array in all ways except the new
arrays were constructed to have C (respectively, F, SC) copula structure for 
the dependences between 
populations in different sampling locations within a simulation. We 
refer to the new arrays as our
*C-copula*, *F-copula*, and *SC-copula population arrays*, respectively. The C-copula array was
constructed as follows; the others were constructed analogously. First, we constructed an
$n$-dimensional C copula with parameter chosen so that the 
Spearman correlations between each pair of the $n$ components were the same as those
of the N distribution constructed above. This was done using the `rho` and `iRho` functions 
in the `copula` package in R. Because the C copula is a one-paremeter family, this 
step relies on the fact that all pairs of locations were 
equally correlated with each other in the original multivariate normal distribution
constructed above. We then randomized each simulation in 
the N-copula population array in a special way 
(see Appendix \ref{sect:copsurrognd}) so that the resulting 
surrogate/randomized dataset had the copula structure
of the C copula just constructed. The randomization procedure worked 
by permuting time series of values in the N-copula array, separately for each 
sampling location and simulation. So population marginal distrbutions for each location
and simulation were *exactly* the same as those in the N-copula population array. 
Permutations were done in such a way
that resulting pairwise Spearman correlations were the same as the C-copula 
constructed above, and hence were the same as the N-copula array, 
except for sampling variation. Thus, to summarize using mathematical notation,
if $m^{(\text{N})}$ is our N-copula population array and $m^{(\text{C})}$ is our 
C-copula population array, then,
for any given $i$ and $j$, the sets $\{m^{(\text{N})}_{tij}: t=1,\ldots,N\}$ and 
$\{m^{(\text{C})}_{tij}: t=1,\ldots,N\}$ are exactly the same (when considered 
as unordered sets); 
and for any given $i_1$, $i_2$ and $j$, the Spearman correlations $\cor_t(m^{(\text{C})}_{ti_1j},m^{(\text{C})}_{ti_2j})$
and $\cor_t(m^{(\text{N})}_{ti_1j},m^{(\text{N})}_{ti_2j})$ are the same, to within 
sampling variation. The whole exercise was repeated preserving Kendall instead of 
Spearman correlations.

A variety of Taylor's law statistics were computed for each simulation $m^{(X)}_{tij}$ 
($i=1,\ldots,n$, $t=1,\ldots,N$) for each copula structure $X$ used. First, the $N=50$ 
spatial means,
$m_t$, and variances, $v_t$, were computed, and $\log(v_t)$ vs. $\log(m_t)$ plots 
were considered. As a shorthand, denote $y=\log(v_t)$ and $x=\log(m_t)$ for a 
single simulation. Linearity of the $y$ vs. $x$ relationship was 
tested for each simulation by comparing the linear regression
through these $50$ points to a quadratic alternative via an $F$-test, 
producing a $p$-value result. If 
these $p$-values were uniformly distributed across the unit interval for the 1000 replicate 
simulations, it supported the linearity assumption of Taylor's law; whereas if 
they were clustered toward smaller values
the test tended to reject that assumption. We also tested, for each simulation, 
the assumption of Taylor's 
law that the $y$ vs. $x$ plot was homoskedastic: we regressed the absolute residuals of the 
linear regression of $y$ versus $x$ against the predictions of that regression. 
A significant $p$-value
result of this test indicates heteroskedasticity. For each simulation we also computed the
root mean squared error of $y$ vs. $x$ data from the linear regression
of $y$ versus $x$, as well as the intercept and slope of the linear regression.
Finally we recorded the quadratic coefficient of the regression of $y$ against
$x$ and $x^2$, and the mean curvature of the quadratic regression equation itself
across the values $x$. The distrubutions of all these statistics across 1000 replicate 
simulations were compared for the C, N, F, and SC simulations to determine if copula structure 
influences Taylor's law.

Taylor's law was strongly influenced, and was often even invalidated in its assumptions of 
linearity and homoskedasticity, by non-N copula structure. For N copula structure 
(i.e., for simulations in our N-copula population array), $p$-values for the linearty
and homoskedasticity tests were roughly uniformly distributed across replicate 
simulations and Taylor's law appeared visually to be a reasonable approximation
of the $\log(v_t)$ versus $\log(m_t)$ relationship (Fig. \ref{fig_spTL}B,E,F). 
Furthermore, quadratic coefficients
and curvature values were close to $0$ (Fig. \ref{fig_spTL}J,K), and root mean squared
errors from the linear regression were relatively small (Fig. \ref{fig_spTL}G).
But linearity or homoskedasticity were violated more frequently for non-N copula structure
(Fig. \ref{fig_spTL}A,C,D,E,F); quadratic coefficients and curvatures were frequently 
non-zero (Fig. \ref{fig_spTL}J,K); and root mean squared
errors from the linear regression were much higher (Fig. \ref{fig_spTL}G). Slopes 
and intercepts of the linear regression were also strongly affected by copula
structure (Fig. \ref{fig_spTL}H,I), though some of the effect here was because
linear regressions do not always adequately represent the $\log(v_t)$ versus $\log(m_t)$
relationship when copula structure was not N.

# Another tool for producing surrogates for multivariate datasets\label{sect:copsurrognd}

\noindent Suppose one has data $x_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$, with
no missing values and no ties, and an
$N$-dimensional copula $C$. The following algorithm produces a surrogate dataset
$y_i(t)$ ($i=1,\ldots,N$, $t=1,\ldots,T$) such that: 1) the Kendall and Spearman 
correlations $\cor_t(y_i(t),y_j(t))$ are the same,
up to sampling variation, as the Kendall and Spearman correlations, respectively, of the corresponding
components of $C$, for all $i\neq j$; and 2) for any $i$, the values of the unordered set 
$\{y_i(t):t=1,\ldots,T\}$ are the same as the values of the unordered set
$\{x_i(t):t=1,\ldots,T\}$.

- Generate data $a_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$ by taking $T$ independent 
draws from $C$.
- For each $k$ and $i$, replace the $k$th-smallest element of the time series $a_i(t)$, 
$t=1,\ldots,T$ by the $k$th smallest element of $x_i(t)$, $t=1,\ldots,T$. Call the 
result $y_i(t)$. This is the surrogate dataset.
